Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-28 acl.2016/acl2016.tex
fixing segfault on thrud

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm (???) with a pop-limit of 400, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employ by users who are sensitive to decoding speed as it gives them the ability to trade speed with translation quality with a simple pop-limit parameter.

>>>>

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm (???) with a pop-limit of 400, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employ by users who require fast decoding as it gives them the ability to trade speed with translation quality with a simple pop-limit parameter.
